\protect\hypertarget{refs}{}
\section{The reference list.}
\protect\hypertarget{ref-aruoba2015}{}Aruoba, S. Borağan, and Jesús Fernández-Villaverde. 2015. \textit{A comparison of programming languages in macroeconomics. }\par
\protect\hypertarget{ref-cabutto2018}{}Ault, Shaun V., Tyler A. Cabutto, Sean P. Heeney, Guifen Mao, and Jin Wang. 2018. \textit{An Overview of the Julia Programming Language. }\par
\protect\hypertarget{ref-besard2018}{}Besard, Tim, Bjorn De Sutter, and Christophe Foket. 2018. \textit{Effective extensible programming: Unleashing julia on gpus. }\par
\protect\hypertarget{ref-bezanson2017}{}Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2017. \textit{Julia: A fresh approach to numerical computing. }\par
\protect\hypertarget{ref-bezanson2012}{}Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2012. \textit{Julia: A fast dynamic language for technical computing. }\par
\protect\hypertarget{ref-udell2014}{}Boyd, Stephen, Steven Diamond, Jenny Hong, Karanveer Mohan, Madeleine Udell, and David Zeng. 2014. \textit{Convex optimization in Julia. }IEEE. \par
\protect\hypertarget{ref-chen2016}{}Chen, Jiahao, and Jarrett Revels. 2016. \textit{Robust benchmarking in noisy environments. }\par
\protect\hypertarget{ref-cusumano-towner2019}{}Cusumano-Towner, Marco F., Alexander K. Lew, Vikash K. Mansinghka, and Feras A. Saad. 2019. \textit{Gen: A general-purpose probabilistic programming system with programmable inference. }New York, NY, USA: ACM. doi:10.1145/3314221.3314642. \href{http://doi.acm.org/10.1145/3314221.3314642}{http://doi.acm.org/10.1145/3314221.3314642}. \par
\protect\hypertarget{ref-lubin2015}{}Dunning, Iain, and Miles Lubin. 2015. \textit{Computing in operations research using Julia. }\par
\protect\hypertarget{ref-edelman2015}{}Edelman, Alan. 2015. \textit{Julia: A fresh approach to parallel programming. }IEEE. \par
\protect\hypertarget{ref-elmqvist2016}{}Elmqvist, Hilding, Toivo Henningsson, and Martin Otter. 2016. \textit{Systems modeling and programming in a unified environment based on Julia. }Springer. \par
\protect\hypertarget{ref-fieker2017}{}Fieker, Claus, William Hart, Tommy Hofmann, and Fredrik Johansson. 2017. \textit{Nemo/Hecke: computer algebra and number theory packages for the Julia programming language. }\par
\protect\hypertarget{ref-innes2018a}{}Fischer, Keno, Dhairya Gandhi, Michael Innes, Neethu Mariya Joy, Tejan Karmali, Avik Pal, Marco Concetto Rudilosso, Elliot Saba, and Viral Shah. 2018. \textit{Fashionable modelling with flux. }\href{http://arxiv.org/abs/1811.01457}{http://arxiv.org/abs/1811.01457}. \par
\protect\hypertarget{ref-ge2018}{}Ge, Hong, Zoubin Ghahramani, and Kai Xu. 2018. \textit{Turing: a language for flexible probabilistic inference. }\href{http://proceedings.mlr.press/v84/ge18b.html}{http://proceedings.mlr.press/v84/ge18b.html}. \par
\protect\hypertarget{ref-innes2018}{}Innes, Michael. 2018. \textit{Don't unroll adjoint: Differentiating SSA-Form programs. }\href{http://arxiv.org/abs/1810.07951}{http://arxiv.org/abs/1810.07951}. \par
\protect\hypertarget{ref-innes2018b}{}Innes, Mike. 2018. \textit{Flux: Elegant machine learning with julia. }doi:10.21105/joss.00602. \par
\protect\hypertarget{ref-masthay2017}{}Masthay, Tyler M., and Saverio Perugini. 2017. \textit{Parareal Algorithm Implementation and Simulation in Julia. }\par
\protect\hypertarget{ref-mogensen2018}{}Mogensen, Patrick Kofod, and Asbjørn Nilsen Riseth. 2018. \textit{Optim: A mathematical optimization package for Julia. }\par
\protect\hypertarget{ref-rackauckas2017}{}Nie, Qing, and Christopher Rackauckas. 2017. \textit{DifferentialEquations.jl – a performant and feature-rich ecosystem for solving differential equations in julia. }doi:10.5334/jors.151. \href{https://app.dimensions.ai/details/publication/pub.1085583166}{https://app.dimensions.ai/details/publication/pub.1085583166}. \par
\protect\hypertarget{ref-novosel2019}{}Novosel, Rok, and Bostjan Slivnik. 2019. \textit{Beyond Classical Parallel Programming Frameworks: Chapel vs Julia. }Schloss Dagstuhl-Leibniz-Zentrum fuer Informatik. \par
